---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rindi1524

<!-- badges: start -->
<!-- badges: end -->

The goal of rindi1524 is to split string.

## Installation

You can install the development version of rindi1524 from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("davyxuximin/rindi1524")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(rindi1524)
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```


```{r}

str_split_one(x, pattern = ",")
```

Use `str_split_one()` when the input is known to be a single string.
For safety, it will error if its input has length greater than one.

`str_split_one()` is built on `stringr::str_split()`, so you can use its `n` argument and stringr's general interface for describing the `pattern` to be matched.

```{r}
str_split_one(x, pattern = ",", n = 2)

y <- "192.168.0.1"
str_split_one(y, pattern = stringr::fixed("."))
```

